Analysis

### 2022-06-06 EDA_CTCFBSDB.Rmd
Quote objects to save

# Save as RData object. subdir is the character name of the CTCF GRanges variable
save(list = hg18.CTCFBSDB.CTCF_predicted_human, file = fileNameOut1)
save(list = mm8.CTCFBSDB.CTCF_predicted_mouse, file = fileNameOut2)
# load(file = paste0(subdir, ".RData"))
# Save BED files
export.bed(hg18.CTCFBSDB.CTCF_predicted_human, fileNameOut1.1)
export.bed(mm8.CTCFBSDB.CTCF_predicted_mouse, fileNameOut2.1)
```

>>>>

# Save as RData object. subdir is the character name of the CTCF GRanges variable
save(list = "hg18.CTCFBSDB.CTCF_predicted_human", file = fileNameOut1)
save(list = "mm8.CTCFBSDB.CTCF_predicted_mouse", file = fileNameOut2)
# load(file = paste0(subdir, ".RData"))
# Save BED files
export.bed(hg18.CTCFBSDB.CTCF_predicted_human, fileNameOut1.1)
export.bed(mm8.CTCFBSDB.CTCF_predicted_mouse, fileNameOut2.1)
```
